---
title: "Second_Blog"
description: This is the second test blog
  A short description of the post.
author:
  - name: Raian Rith
    url: https://www.linkedin.com/in/raian-rith/
date: 2022-05-01
output:
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE} 
knitr::opts_chunk$set(echo = FALSE) 
```



```{r}
library(tidyverse)
library(readxl)
library(plotly)
library(dplyr)
```

```{r}
df <- read_excel("state_count(econ,bio,psych).xlsx")
```



```{r}
df_bio <- df %>% select(Full_State,state, count_bio, perc_bio)
df_bio$perc_bio1 <- df_bio$perc_bio*100
df_bio <- df_bio %>% select(Full_State, state, count_bio, perc_bio1)
df_bio$round_perc <- round(df_bio$perc_bio1 ,digit=2)
df_bio <- df_bio %>% 
                select(Full_State,state, count_bio, percentage_of_alum = round_perc) %>%
                mutate(hover = paste0(Full_State, "\n", percentage_of_alum, "%"))
```

```{r}

fontStyle = list(
  size = 15,
  color = "black"
)

label = list(
  bgcolor = "#EEEEEE",
  bordercolor = "transparent",
  font = fontStyle
)

bio_graph <- plot_geo(df_bio,
                       locationmode = 'USA-states') %>%
  add_trace(locations = ~state,
            z = ~percentage_of_alum,
            zmin = 0,
            zmid = 15,
            color = ~percentage_of_alum, 
            colorscale = 'Greens',
            reversescale = TRUE,
            text = ~hover,
            hoverinfo = 'text') %>%
  layout(geo = list(scope ='usa'),
         title = "Lawrence Alums Working in USA\n(Majored in Biology)") %>%
  colorbar(tickprefix =  "(%) ")

bio_graph
```



Distill is a publication format for scientific and technical writing, native to the web.

Learn more about using Distill at <https://rstudio.github.io/distill>.

This html file provides choropleth maps based on the percentage of Lawrence alumnis who accepted jobs/researches in various states around the US. Data has been collected by the Career Center, Lawrence University. The maps are interactive - hover over them to reveal the name of the state and the percentage of Lawrence alums working there. 

The top 5 majors based on data are as follows:

1) Biology - 309 Students

2) Psychology - 250 Students

3) Economics - 233 Students

4) English - 203 Students

5) Government - 184 Students



## Lawrence Alumnis who majored in Biology (Map of 309 Students)

The graph below shows the percentage of Lawrence alumni working around the United States who had majored in Biology during their time at Lawrence. The maps are interactive - hover over them to reveal the name of the state and the percentage of Lawrence alums working there. 


```{r eval = TRUE}
library(tidyverse)
ggplot(mtcars, aes(hp,mpg)) + 
  geom_point() + 
  geom_smooth() + 
  theme_bw()
```